Untitled

### 2014-11-29 Misc/TrialFile.Rmd
Temporary fix for GEM data cleaning

>>>>

CleanMerge <- cbind(names = c(rownames(Clean01), rownames(Clean02), rownames(Clean03),
                              rownames(Clean04), rownames(Clean05), rownames(Clean06),
                              rownames(Clean07), rownames(Clean08), rownames(Clean09),
                              rownames(Clean10)),
                    rbind.fill(list(Clean01, Clean02, Clean03, Clean04, Clean05, Clean06,
                                    Clean07, Clean08, Clean09, Clean10)))

# Change merged data from wide to long
LongGEM<- melt(data = Merged9,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

# Rename columns
names(LongGEM) <- gsub("variable", "Year", names(LongGEM))
names(LongGEM) <- gsub("value", "Support", names(LongGEM))

# Create a vector with OECD countries
myvars <- c('Australia', 'Austria', 'Belgium', 'Canada', 'Chile', 'Czech Republic', 'Denmark', 'Estonia', 'Finland', 'France', 'Germany', 'Greece', 'Hungary', 'Iceland', 'Ireland', 'Israel', 'Italy', 'Japan', 'South Korea', 'Luxemburg', 'Mexico', 'Netherlands', 'New Zealand', 'Norway', 'Poland', 'Portugal', 'Slovak Republic', 'Slovenia', 'Spain', 'Sweden', 'Switzerland', 'Turkey', 'United Kingdom', 'United States')

# Subset LongGEM with the countries we need
subset_data <- subset(LongGEM, Country %in% myvars)

# Delete unnecessary column
subset_data$row.names <- NULL

# Arrange subset_data by country and year
GrandData <- arrange(subset_data, Country, Year)

GrandData1 <- GrandData[order("Country",)]

########### STUCK #############

FinalData <- merge(FinalGEM, GrandData,
                   union("Country", "Year"))
```
